\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{authblk}

%\newcommand{\todo}[1]{\color{red}\textbf{\hl{#1}}\color{black}\xspace}
%\newcommand{\todo}[1]{}

\title{Survey: Quantum Computing Algorithms and Programming Model}
\author[]{Md Maruf Hossain \\ mhossa10@uncc.edu}
\affil[]{Department of Computer Science, UNC Charlotte}
\date{}

\begin{document}
\maketitle

I want to present a survey on \textit{Quantum Computing} algorithm and programming model as a course project.
I will work on this project by myself, so there is no need of work distribution. In this proposal, 
I will give you the motivation and goal of the survey. And also the time plan of the project. 

\section{Motivation}
Quantum computing is now one of the most popular and growing sectors in modern science. The main reason behind this 
is the performance capability of the quantum computer. For example, Shor's~\cite{shor1994algorithms} algorithm to find 
the prime factors of integer $N,$ it can give you output in polynomial($log N$) time. This kind of example boosts up the 
confidence of computing on the quantum computer. But it is not so straight forward like a traditional computer. Different algorithms 
need different insight to accommodate into the quantum computer. On the other hand, the programming language 
of quantum computing is not that much matured as traditional language. The main purpose of the survey is to discuss 
the different quantum algorithms ~\cite{shor1994algorithms}~\cite{simon1997power}~\cite{gall2014improved}
and their performance against existing traditional algorithms. And also analyze the different quantum programming languages 
~\cite{knill1996conventions}~\cite{selinger2004towards}~\cite{bettelli2003toward}~\cite{omer1998procedural}~\cite{sanders2000quantum} 
that one can get a clear concept of quantum algorithm what kind of languages best for them.

\section{Goal}
\begin{enumerate}
\item Write a survey on different quantum computing algorithms and compare them with the traditional algorithm.
\item Discuss different quantum programming languages.
\item Try to find out a clear concept that what kind of algorithm suitable for quantum computing and what kind 
of programming language one should choose.
\item Make a presentation on the survey to present in the class.
\end{enumerate}

\section{Shcedule of the Project}
Here is the task and their schedule of the project,
\begin{table}[htb]
  \small
\caption{Time Sheet}
\label{tab:timesheet}
\centering
\begin{tabular}[c]{| l | l | c|}
\hline
Date & Task & Overall Percentage \\ \hline
02/19/2019 & Project Proposal & 10\% \\ \hline
03/19/2019 & Mid-Term Report & 50\% \\ \hline
04/16/2019 & Slides of Survey & 90\% \\ \hline
04/30/2019 & Final Report & 100\% \\ \hline
\end{tabular}
\end{table}

\bibliographystyle{unsrt}
\bibliography{reference}


\end{document}
